---
title: "&nbsp;"
output:
    md_document
---

```{r setup, include = FALSE} 
base_fig_height <- 4
knitr::opts_chunk$set(warning = FALSE, message = FALSE, error = FALSE,
                      fig.width = 12, fig.height = base_fig_height, dpi = 300)
```

# SpatialFeaturePlotBlend

An implementation of Seurat's `SpatialFeaturePlot` that allows the expression
of two features to be displayed simultaneously and in relation to one another.

## Code

Available in [SpatialFeaturePlotBlend.R](SpatialFeaturePlotBlend.R).

## Usage

<details>
<summary>
We use the `brain` dataset from the Seurat spatial vignette as an example
dataset. Click to reveal its processing.
</summary>

```{r load_example_data}
brain <- SeuratData::LoadData("stxBrain", type = "anterior1")
brain <- Seurat::SCTransform(brain, assay = "Spatial", verbose = FALSE)
```

</details>

```{r basic_plot}
library(Seurat)
library(ggplot2)
library(dplyr)
library(patchwork)
source("SpatialFeaturePlotBlend.R")

SpatialFeaturePlotBlend(object = brain, features = c("Hpca", "Ttr"))
```

## Other options

### Custom colors

You can choose which colors to use by specifying them as follows:

```{r custom_colors}
    SpatialFeaturePlotBlend(object = brain, features = c("Hpca", "Ttr"),
                            top_left = "blue", bottom_right = "orange",
                            bottom_left = "white", top_right = "#FF0000")
```

### Multiple images

A `Seurat` object containing multiple images can be used as follows:

<details>
<summary>
We load another member of the `brain` dataset. Click to reveal its processing.
</summary>

```{r load_more_example_data}
brain2 <- SeuratData::LoadData("stxBrain", type = "posterior1")
brain2 <- Seurat::SCTransform(brain2, assay = "Spatial", verbose = FALSE)
```

</details>

```{r multiple_images, fig.height = 2 * base_fig_height}
brain_merged <- merge(x = brain, y = brain2)
SpatialFeaturePlotBlend(object = brain_merged, features = c("Hpca", "Ttr"))
```

Notes:

* The color scales of each image are independent.
* `SpatialFeaturePlotBlend` assumes that the spots in the data of `object` are
  grouped together in the same order as the image names in `Images(object)` (as
  should happen following `merge`).  If this assumption is violated, then
  strange things might happen...

### Non-default assays

Non-default assays can be plotted using the `assay` argument:

```{r non_default_assays}
SpatialFeaturePlotBlend(object = brain, features = c("Hpca", "Ttr"),
                        assay = "Spatial")
```

### Alternative feature names

Alternative names for `feature_1` and `feature_2` can be passed as
`feature_1_alt_name` and `feature_2_alt_name`, respectively. Currently, these
alternative names are only used in labelling the legend.

```{r alternative_feature_names}
SpatialFeaturePlotBlend(object = brain, features = c("Hpca", "Ttr"),
                        feature_1_alt_name = "Hpca_alias")
```

### Additional arguments

Additional arguments can be passed to the underlying plotting functions. For
example, we can change `alpha`:

```{r additional_arguments}
SpatialFeaturePlotBlend(object = brain, features = c("Hpca", "Ttr"),
                        alpha = 0.5)
```

## Bugs

There are probably bugs in this implementation and it has not been rigorously
tested, so please use at your own risk! If you do identify a bug, please submit
it as an issue
[here](https://github.com/george-hall-ucl/SpatialFeaturePlotBlend/issues).

## Licensing

<details>
<summary>Click to reveal licensing information</summary>
    Copyright (C) 2024 University College London, licensed under GNU General
    Public License v3.0.

    This program is free software: you can redistribute it and/or modify it
    under the terms of the GNU General Public License as published by the Free
    Software Foundation, either version 3 of the License, or (at your option)
    any later version.

    This program is distributed in the hope that it will be useful, but WITHOUT
    ANY WARRANTY; without even the implied warranty of MERCHANTABILITY or
    FITNESS FOR A PARTICULAR PURPOSE.  See the GNU General Public License for
    more details.

    You should have received a copy of the GNU General Public License along
    with this program.  If not, see <http://www.gnu.org/licenses/>.
</details>
